---
title: "Cereales"
author: "Diana Marcela Beltrán Pedroza"
date: "2025-09-30"
output: pdf_document
---


```{r}
# install.packages("readxl")
library(readxl)
library(dplyr)

```
```{r}
cereal <- read_excel("cereal.xlsx")
head(cereal)


```
**Q1 Extract rows 1 to 10 from the cereal data frame. (Extraiga las filas 1 a 10 del marco de datos cereal.)**

```{r}
cereal[1:10, ]

```
**Q2**

```{r}
# data frane

Kelloggs <- cereal[cereal$company == "K",]
head(Kelloggs)

```
**Q3**

```{r}

cereal[cereal$sugars > 10, "name"]
```
 **Q4**
 
```{r}

mean(cereal$calories)
```
 **Q5**
 
```{r}
subset(cereal, fiber >= 2)
```
 
 **New practice **
 
```{r message=FALSE, warning=FALSE, paged.print=TRUE}
EquationCitations <- read.csv("EquationCitations.csv")
head(EquationCitations)
```
 
 **Q1 On average, how many equations per article are published in each journal? (Hint: use group_by() and summarise())** 
 
```{r}
EquationCitations %>%
  group_by (journal) %>%
  summarize(promedio = mean(equations))
```
 
 
**Q2 For each journal, calculate the average proportion of theoretical citations relative to total citations. (Hint: create a new column with mutate(theo_ratio = theocites / cites), then group_by() and summarise())**
## Para cada revista, calcule la proporción promedio de citas teóricas respecto al total de citas. (Sugerencia: cree una nueva columna con mutate(theo_ratio = theocites / cites), luego group_by() y summarise())

```{r}
EquationCitations %>%
  mutate(theo_ratio = theocites / cites) %>% 
  group_by(journal) %>% 
  summarise(citaspromedio = mean(theo_ratio))
```

