---
title: "Homework1"
author: "Diana Marcela Beltrán Pedroza"
date: "2025-09-04"
output: html_document
---
## Assigning values

**Q1. Create an object called height with the value 175. Print it. (Crea un objeto llamado height con el valor 175. Muéstralo en pantalla.)**

```{r}
Altura <- 175
Altura
```
## Simple math

**Q2. Calculate the result of 25 * 4 - 10. (Calcula el resultado de 25 * 4 - 10.)**
```{r}
25 * 4 - 10
```
## Using functions

**Q3. Use the function sqrt() to calculate the square root of 81. (Usa la función sqrt() para calcular la raíz cuadrada de 81.)** 
```{r}
sqrt(81)
```
## Character objects

**Q4. Assign the phrase “R is fun!” to an object called message. Print it. (Asigna la frase “R is fun!” a un objeto llamado message. Muéstralo.)**

```{r}
my_obj1 <- "R is fun"
my_obj1

```
## Object manipulation

**Q5. Create two objects a <- 10 and b <- 5. Calculate their sum and store it in c. (Crea dos objetos a <- 10 y b <- 5. Calcula su suma y guárdala en c.)**

```{r}
a <- 10
b <- 5
c <- a + b
c
```
## Logical comparison

**Q6. Test whether 15 is greater than 20. (Verifica si 15 es mayor que 20.)**


```{r}
15 > 20
```

```{r}
class("Hello world")
```

```{r}
##log(-1)
```


```{r}
##log(-1)
```



```{r}
##library(dplyr)
```
```{r}
##library(dplyr)
```

```{r}
?mean()
```







